\documentclass[10pt,colorlinks=true,urlcolor=teal]{moderncv}
\usepackage{utopia}
\moderncvtheme[green]{classic}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage[resetlabels]{multibib}
\newcites{pre,peer,conf,pres,talks,other,prog,unp}{%
 , % Pre-prints
 , % Peer Reviewed Articles
 , % Conference Proceedings
 , % Posters
 , % Talks
 % Other Publications
 ,
 ,
}
\renewcommand{\bibliographyitemlabel}{\@{\arabic{enumiv}}}

\usepackage[scale=0.8]{geometry}
\newcommand{\cvdoublecolumn}[2]{%
  \cvline{}{}{%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#1\end{minipage}%
    \hfill%
    \begin{minipage}[t]{\listdoubleitemmaincolumnwidth}#2\end{minipage}%
    }%
}
%
% usage: \cvreference{name}{address line 1}{address line 2}{address line 3}{address line 4}{e-mail address}{phone number}
% Everything but the name is optxional
% If \addresssymbol, \emailsymbol or \phonesymbol are specified, they will be used.
% (Per default, \addresssymbol isn't specified, the other two are specified.)
% If you don't like the symbols, remove them from the following code, including the tilde ~ (space).

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3}%
    \ifthenelse{\equal{#4}{}}{}{#4}%
    \ifthenelse{\equal{#5}{}}{}{#5}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7\newline}}

  \AtBeginDocument{\recomputelengths} 
  \firstname{Gregory S.~}
  \familyname{Kiar} 
  \address{2723 Saint Paul St., Apartment 2\\ }{Baltimore, MD, 21218} 
  \email{gkiar@jhu.edu}
  \phone{443-554-6865}
  \extrainfo{\homepagesymbol~\textnormal{\href{http://gkiar.github.io}{gkiar.github.io}} \textnormal{|}\githubsocialsymbol~\textnormal{\href{http://github.com/gkiar}{gkiar}}}
\begin{document}
\maketitle

\section{Education}
\cventry{2014 -- 2016}{M.S.E. in Biomedical Engineering}{\newline Johns Hopkins Whiting School of Engineering, supervised by Joshua Vogelstein}{}{}{\textit{Thesis:} GREMLIN: Graph Estimation from MR images Leading to Inference in Neuroscience.}
\cventry{2010 -- 2014}{B.Eng in Biomedical and Electrical Engineering}{\newline Carleton University, supervised by Leonard MacEachern, Andrew Adler, and Rafik Goubran}{}{}{\textit{Capstone:} Electrical muscle stimulation with concurrent EMG feedback of the upper arm for applications in stroke rehabilitation}
\cventry{09/16 -- 10/16}{Exploring the Human Connectome}{The Human Connectome Project, Boston, MA, USA}{}{}{}
\cventry{10/15 -- 10/15}{Presenting Data and Information}{Edward Tufte, Baltimore, MD, USA}{}{}{}

\section{Academic Experience}

\subsection{Current Positions}

\cventry{09/14 -- now}{Research Engineer}{Center for Imaging Science, Johns Hopkins University}{}{}{Development and maintenance of an open-source pipeline for multi-scale brain-graph generation from human MR images. Implementation and development statistical algorithms for quality control of data derivatives. Publicly release data products to lower the barrier to entry for neuroscience research.}
\cventry{09/14 -- now}{Teaching Assistant}{Dept. of Biomedical Engineering, Johns Hopkins University}{}{}{Responsible for instruction, evaluation, and content design for: Freshman Modeling and Design for BME (2014, 2015), Systems and Controls (2015), Statistical Connectomics (2015), The Art of Data Science (2016), NeuroData Design (2016). Has spent more than 500 hours (cumulative) working with students.}

\subsection{Current Activities}
\cventry{09/14 -- now}{Chief Neurocartographer and Core Team Member}{NeuroData}{\textnormal{\url{http://neurodata.io}}}{}{Performer on core research objectives. Chiefly responsible for content curation and presentation of grant deliverables to funding agency. Manager and organizer of public presence and conferences.}

\subsection{Previous Positions}
\cventry{01/15, 01/16}{Instructor}{Dept. of Computer Science, Johns Hopkins University}{}{}{Responsible for instruction, evaluation, and content design for intensive 3-week project-based course on an introduction to connectomics research across multiple scales and experimental modalities.}
\cventry{09/12 -- 05/14}{Facilitator for Peer-Assisted Study Sessions}{Student Academic Success Center, Carleton University}{}{}{Instructed and demonstrated mastery of principles in electromagnetism and power engineering.}
\cventry{08/13 -- 05/14}{Facilitator Team Leader}{Student Academic Success Center, Carleton University}{}{}{Provided training, mentoring, and coaching to student instructors in a variety of disciplines.}
\cventry{01/13 -- 06/14}{Teaching Assistant}{Dept. of Systems and Computer Engineering, Carleton University}{}{}{Instructed introductory level C++ programming.}

\section{Work Experience}
% \cventry{09/13 -- 08/14}{Consultant}{Self-employed}{}{}{Developed data analysis tools, computer systems infrastructure, and websites for several university departments.}
\cventry{06/13 -- 09/13}{Research Assistant under Dr. Rafik Goubran}{Dept. of Biomedical Engineering, Carleton University}{}{}{Developed wireless medical data publish-subscribe system for viewing patient vital signs remotely.}
\cventry{06/12 -- 09/12}{Research Assistant under Dr. Andy Adler}{Dept. of Systems and Computer Engineering, Carleton University}{}{}{Utilized neural networks for inverse modeling of real and simulated biological systems.}
\cventry{06/11 -- 09/11}{Research Assistant under Dr. Jeffrey Dawson}{Dept. of Biology, Carleton University}{}{}{Developed robotics platform for studying insect locomotion patterns and behaviour.}
\cventry{01/09 -- 09/09}{Research Assistant under Dr. Jim Dimitroulakos}{CRC, Ottawa Hospital Research Institute}{}{}{Tested combination therapies of Lovastatin and Cisplatin drugs on colon and breast cancer strains.}

\section{Volunteer Experience}
\cventry{06/15 -- 09/16}{College Mentor \& Essay Reviewer}{College Prep Program}{}{}{}
\cventry{09/14 -- 06/16}{Grandparent \& Volunteer}{Thread (formerly Incentive Mentoring Program)}{}{}{}
\cventry{06/13 -- 05/14}{President}{Carleton University Biomedical Engineering Society}{}{}{}
\cventry{09/13 -- 06/14}{Co-Founder and Vice President}{PASS Talks}{}{}{}
\cventry{12/12, 12/13}{Navigator and Driver}{Operation Red Nose Ottawa}{}{}{}
\cventry{09/10 -- 09/11}{Emergency First Responder}{Carleton University Student Emergency Response Team}{}{}{}

\section{Skills}
\cventry{Languages}{English, American Sign Language (basic)}{}{}{}{}
\cventry{Coding}{MATLAB, Python, R, LaTeX, HTML/CSS, x86 and ARM assembly}{}{}{}{}
\cventry{Soft skills}{Leadership, problem-solving, clear and effective communication, design}{}{}{}{}{}

\section{Awards \& Honors}
\cventry{2014}{Greatest Social Impact Paper}{Professional Engineering Ontario (PEO)}{}{}{}
\cventry{2014}{ SEED Fund}{Carleton University Engineering Alumni}{}{}{}
\cventry{2014}{IEEE Papers Showcase Local Winner}{IEEE Ottawa-Carleton Chapter}{}{}{}
\cventry{2014}{IEEE Papers Showcase Provincial Runner-up}{IEEE}{}{}{}
\cventry{2014}{Carleton Electronics Project Competition Champion}{Carleton University}{}{}{}
\cventry{2013}{Engineering '65 and '66 Scholarship}{Carleton University}{}{}{}
\cventry{2012--2014}{Dean's Honour List}{Carleton University}{}{}{}
\cventry{2012}{Clarence C. Gibson Scholarship}{Carleton University}{}{}{}


% \begin{comment}
\section{Under Review Pre-Prints}
\vspace{-15pt}
\nocitepre{Kiar2016, vogelstein2016:grandchallenges, Gorgolewski2016:bids}
\bibliographystylepre{unsrtinit}
\bibliographypre{gkiar}
% \end{comment}

% \begin{comment}
\section{Peer-Reviewed Journal Publications}
\vspace{-15pt}
\nocitepeer{neurostorm}
\bibliographystylepeer{unsrtinit}
\bibliographypeer{gkiar}
% \end{comment}

\section{Peer-Reviewed Conference Proceedings}
\vspace{-15pt}
\nociteconf{Kiar2013}
\bibliographystyleconf{unsrtinit}
\bibliographyconf{gkiar}

%\begin{comment}
\section{Work in Progress -- Pre-prints Available upon Request}
\vspace{-15pt}
\nociteprog{vogelstein2016:nd, kiar2016x, grayroncal2016:wm, wang2016:discriminability}
\bibliographystyleprog{unsrtinit}
\bibliographyprog{gkiar}
%\end{comment}

% \begin{comment}
\section{Other Publications}
\vspace{-15pt}
\nociteother{ndmgcode}
\bibliographystyleother{unsrtinit}
\bibliographyother{gkiar}
% \end{comment}

\begin{comment}
\section{Unpublished Work}
\vspace{-15pt}
\nociteunp{}
\bibliographystyleunp{unsrtinit}
\bibliographyunp{gkiar}
\end{comment}

\begin{comment}
\section{Invited Talks}
\vspace{-15pt}
\nocitetalks{}
\bibliographystyletalks{unsrtinit}
\bibliographytalks{gkiar}
\end{comment}

\section{Poster Presentations}
\vspace{-15pt}
\nocitepres{Kiar2016a, Vogelstein2015a, Kiar2015a}
\bibliographystylepres{unsrtinit}
\bibliographypres{gkiar}


\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
%
~